\section{Executive Summary: The Work Must Outlive the Chat}

\textbf{The session is the right unit of interaction---and the wrong unit of
continuity for long-running Agent work.} A session can host valuable code,
research, plans, operations, and decisions. It cannot, by itself,
authoritatively settle what the project has become, what was accepted, which
authority still applies, or where another participant may safely continue.
When the session closes, a transcript, summary, or unverified memory is not
enough. The model may be capable while the work remains fragile.

Kungfu closes this gap through three distinct layers. A \textbf{Project Cut}
is the verifiable settlement and continuation coordinate presented to the
next human or Agent. \texttt{libkungfu} is the local runtime that records,
verifies, recovers, and resumes that continuity inside a participant's Hub.
KFD is the open responsibility protocol that lets independently owned Hubs
exchange continuity evidence without sharing one central cloud or surrendering
their product boundary.

Together, these products provide the founding proof for an open Agent Supply
Chain. KFD-3 makes product cooperation discoverable; Buildchain binds product
claims to exact software artifacts; KFD-2 supports purpose-bound trust;
libkungfu and \texttt{.kungfu} preserve durable work facts; and the public KFD
Agent Hub profile lets independently owned Hubs carry bounded responsibility
objects without sharing one vendor control plane.

This is a second strategic axis, not a claim that a multi-Hub market already
exists. The current evidence covers public contracts, release mechanics,
source-built runtime slices, and first-party qualification. It does not prove
two independent production Hubs, external vendor adoption, industry-standard
status, or blanket stable interoperability.

A Project Cut binds the accepted source state, the perspective used to
understand it, the causal work that occurred, the decisions that admitted the
result, unresolved risk, and the coordinate from which authorized work may
continue. It does not replace those authorities. It gives the next participant
one bounded answer to the question: \emph{where can this project safely
continue?}

\calloutbox{The product promise}{Give your agent verified context. Keep the
work when the chat ends.}

\subsection{One Product Decision, Two Adoption Paths}

Users should encounter Project Cut continuity before they need to understand
the runtime beneath it. Agent builders, however, need an immediate technical
path. Kungfu therefore separates two responsibilities:

\begin{enumerate}
  \item embed \texttt{libkungfu} as the reference runtime for durable Facts,
  Episodes, verification, recovery, and Project Cut continuity; and
  \item build a participant-owned Hub that retains the vendor's user
  experience, models, identity, accounts, policies, cloud, admission rules,
  and customer relationship while exchanging portable responsibility evidence
  through KFD.
\end{enumerate}

These paths should proceed in parallel. A vendor does not need to rebuild a
journal, content-addressed evidence store, recovery engine, and cross-language
fact layer before delivering continuity. Nor should embedding a runtime force
the vendor to surrender its product boundary to a central Kungfu service.

\calloutbox{Recommended Agent Builder strategy}{Build your Hub. Do not rebuild
the runtime. Embed libkungfu now, prove one source-pinned Project Cut
loop, and develop your KFD-compatible Hub boundary in parallel.}

\subsection{The Architecture in Five Responsibilities}

\begin{tabularx}{\textwidth}{>{\bfseries\raggedright\arraybackslash}p{0.21\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Project Cut & The project settlement and continuation coordinate presented to
users and Agents. \\
\texttt{libkungfu} & The reference implementation for runtime Facts, Episodes,
journal authority, verification, export, and recovery. \\
KFD & The open engineering standard for responsibility, evidence, trust, and
continuity across independently implemented systems. \\
Buildchain & Artifact, provenance, release, and evidence publication; not
runtime or project authority. \\
Vendor Agent Hub & Product experience, models, identity, policy, accounts,
admission, cloud, and customer relationship. \\
\bottomrule
\end{tabularx}

\subsection{What This Paper Claims}

Kungfu provides a concrete architecture, open source implementation, and
first-party evidence for work that survives session and Agent replacement. It
does not claim that a transcript is a Project Cut, that delivery is admission,
that an Episode proves completion, or that authentication grants authority. It
does not claim external vendor adoption, stable KFD Hub interoperability,
certification, or broad production readiness. The public interfaces described
here are alpha surfaces and should be adopted through exact source and evidence
coordinates.
