\section{The Continuity Gap}

Real work is not a prompt-response pair. It has accepted state, causal history,
direction, authority, evidence, unresolved conflict, and consequences. It may
cross context windows, models, devices, repositories, organizations, and years.
A session is only one observer's temporary projection of that work.

This creates a product failure that better models alone cannot solve. A capable
Agent can finish an action and still leave the project unable to continue. A
new session may know what was said without knowing what was accepted; see a
commit without knowing why it was chosen; inherit a task without inheriting the
authority to perform it; or receive a confident summary that silently omits a
conflict.

\subsection{Context Is Not Project State}

Common continuity mechanisms are useful but insufficient on their own:

\begin{tabularx}{\textwidth}{>{\bfseries\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Chat transcript & Preserves conversation, not admission, authority, or a
deterministic project boundary. \\
Generated summary & Compresses context, but may hide loss, mix observation with
decision, or drift when regenerated. \\
Vector memory & Helps recall, but similarity is not causality, acceptance, or
permission. \\
Git history & Preserves source content and ancestry, but not the complete
perspective, Episode, trust decision, or continuation Warrant. \\
Workflow database & Coordinates mutable process state, but does not necessarily
publish an independently verifiable settlement. \\
Vendor session cloud & Can preserve provider context, but may strand continuity
inside one product and one account boundary. \\
\bottomrule
\end{tabularx}

The missing object is not ``more memory.'' It is an explicit, bounded
commitment about the project.

\subsection{What a Successor Agent Needs}

A fresh Agent should be able to determine, without trusting the previous
session's prose:

\begin{itemize}
  \item the exact project settlement from which it is continuing;
  \item which source, perspective, causal, policy, and decision authorities the
  settlement binds;
  \item what work occurred and what result was actually admitted;
  \item what remains unknown, omitted, conflicted, rejected, or intentionally
  withheld;
  \item which continuing direction and bounded authority apply now; and
  \item how to verify the record and publish a successor without rewriting
  history.
\end{itemize}

This is the continuity gap Kungfu is designed to close. The product measure is
not session length. It is whether one participant can hand real work to another
through an exact, inspectable boundary with less human reconstruction and no
silent expansion of trust.
