\section{The Strategic Choice for Agent Builders}

An Agent vendor already owns the scarce product assets: the interface, model
experience, accounts, permissions, policies, cloud, distribution, and customer
relationship. It should preserve those assets. The strategic question is not
whether to become a Kungfu-branded application. It is whether to spend years
reconstructing a durable runtime before its users can keep work across chats.

The recommended answer is direct:\cite{kungfuBuilders}

\calloutbox{Build your Hub. Do not rebuild the runtime.}{Embed
libkungfu now to deliver Project Cut continuity. In parallel, build
your own KFD-compatible Hub so responsibility can move across products without
moving product ownership.}

\subsection{The Two-Track Plan}

\textbf{Track A---embed the runtime.} Pin an exact \texttt{libkungfu} source
coordinate, integrate the smallest C, Node, or Python path, keep provider data
and credentials outside the adapter, and prove one complete local loop: inspect
a Project Cut, record bounded work, verify the evidence, settle a successor,
and continue from it in a fresh Agent context.

\textbf{Track B---build the Hub.} Retain participant-owned identity, policy,
admission, storage, product workflow, and customer controls. Add a KFD adapter
that can negotiate exact capabilities, exchange rooted responsibility objects,
write receiver-owned verdicts, preserve conflicts and disclosure boundaries,
and export portable evidence.

The two tracks reinforce each other. Runtime integration creates immediate user
value and real implementation evidence. Hub development prevents that value
from becoming a local island. Waiting for a finished network before embedding
the runtime delays the product; rebuilding the runtime before designing the Hub
duplicates infrastructure without solving interoperability.

\subsection{The Ownership Boundary}

\begin{tabularx}{\textwidth}{>{\bfseries\raggedright\arraybackslash}p{0.25\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Keep in the vendor Hub & UX, models, prompts, tool policy, accounts, billing,
identity mapping, customer data, cloud, admission decisions, and support. \\
Embed from \texttt{libkungfu} & Local runtime Facts, Episodes, journal and
content roots, lifecycle, query, verification, export, recovery, and Project
Cut substrate. \\
Exchange through KFD & Exact profile coordinates, capability roots,
responsibility references, evidence, disclosure state, verdicts, conflicts,
and residual risk. \\
Publish through Buildchain & Artifact digests, source coordinates, build and
release provenance, release claims, and residual release risk. \\
\bottomrule
\end{tabularx}

\subsection{What Embedding Does and Does Not Mean}

Embedding \texttt{libkungfu} provides Kungfu's reference runtime
implementation for KFD-governed Facts, Episodes, responsibility boundaries,
verification, recovery, and Project Cut continuity. It is the fastest route to
an executable implementation and the default recommendation for Agent
builders.

It does not make KFD proprietary, force one Hub design, send data to a required
Kungfu cloud, or automatically certify conformance. KFD remains open and
independently implementable. Every compatibility claim must stay bound to the
exact Profile, implementation, suite, platform, evidence, and residual risk
that were actually assessed.
