\section{Project Cut: The First User Object}

The first user layer in Kungfu is not a log viewer, model selector, or internal
Fact table. It is the Project Cut: the highest ordinary interface through which
a person or Agent inspects what a project has formally become and from where it
may continue. This product decision keeps rigor below the surface while giving
the user one actionable coordinate above it.\cite{kungfuProjectCut}

\subsection{What a Project Cut States}

A Project Cut binds the following without replacing any of them:

\begin{tabularx}{\textwidth}{>{\bfseries\raggedright\arraybackslash}p{0.25\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Predecessor & The exact prior Project Cut or Cuts from which this settlement
descends. \\
Source projection & The accepted Git or other source coordinate, under the
source system's own authority. \\
Atlas & The declared perspective, sources, loss, and context used to interpret
the project. \\
Episode increment & The admitted causal occurrence boundary: what happened,
not merely what state now exists. \\
Decision and policy & The rules, Claims, Assessments, authorized Decisions, and
Admission boundary used to accept the result. \\
Open boundary & Known omissions, conflicts, unknowns, rejected claims,
withholding, and residual risk. \\
Continuation & The continuing Initiative or Pursuit, bounded Assignment and
Warrant coordinates, verifiable root, and non-self-certifying receipt. \\
\bottomrule
\end{tabularx}

The result answers four user questions at once: What did the project officially
become? What happened to produce that state? What was accepted rather than
merely delivered or claimed? Where may authorized work continue?

\subsection{A Settlement, Not a Fourth Fact Engine}

The source repository remains authoritative for source. An Atlas or another
perspective system remains authoritative for its declared context. The Kungfu
runtime remains authoritative for admitted Facts and Episodes. Policy and
decision authorities remain independently accountable for Admission. The
Project Cut verifies and binds those roots; it does not absorb, reinterpret, or
silently synchronize them.

This separation is essential. A large merged ``project state'' object would be
easy to display but difficult to challenge, recover, or independently verify.
A Project Cut instead publishes a deterministic macro commitment at an outer
project coordinate while retaining the ability to inspect each authority and
to reject a stale, missing, conflicted, unverifiable, or circular binding.

\subsection{Why It Comes First}

Users should not need to understand every Fact, Episode, Atlas source, Warrant,
or receipt before resuming ordinary work. They should see the current verified
Cut, active direction, bounded work, pending candidate, and actionable
problems. Deeper evidence remains available when a decision, audit, failure, or
high-consequence action requires it.

Project Cut is therefore a progressive-disclosure boundary. It compresses
complexity without pretending the complexity disappeared. Product work should
optimize time-to-first-cut and cut-to-cut continuity, not the number of kernel
primitives visible in the interface.

\subsection{Validity Is Not Completion}

A structurally valid Project Cut proves that declared roots bind and verify
under the stated protocol. It does not by itself prove that every objective is
complete, the result is correct, the work is safe, or a release is fit for
production. Those are explicit Claims and Assessments owned by their declared
decision authorities. Project Cut preserves the conclusion and its boundary;
it does not manufacture one.
