\section{How Work Continues Across Sessions}

Continuity is a closed loop, not a saved transcript. Kungfu's target product
loop is:\cite{kungfuProjectCut}

\begin{enumerate}
  \item inspect and verify the current Project Cut;
  \item accept bounded work in a continuing Initiative or Pursuit, against the
  exact Atlas and Warrant roots;
  \item execute while preserving causal occurrence in an Episode;
  \item submit a completion or state-change Claim with evidence;
  \item independently assess the Claim and record the authorized Decision;
  \item admit only the accepted result and prepare a candidate successor Cut;
  \item verify and explicitly settle the exact candidate; and
  \item start a fresh session or Agent from that successor Project Cut.
\end{enumerate}

In short:

\begin{center}
\textbf{session ends $\rightarrow$ Project Cut remains $\rightarrow$ fresh
Agent verifies $\rightarrow$ work occurs $\rightarrow$ Episode records
$\rightarrow$ Claim is decided $\rightarrow$ result is admitted
$\rightarrow$ successor Cut is published}
\end{center}

\subsection{Agent Supply Chain}

The public architecture separates five responsibilities that products often
rebuild inside one private control plane:

\begin{enumerate}[leftmargin=*]
  \item KFD-3 exposes value, constraints, choices, commands, Exit, and records
  so products can discover how to cooperate.
  \item Buildchain binds product-owned declarations to an exact source cut,
  build, artifacts, checks, and promotion evidence.
  \item KFD-2 lets a receiver assess those claims for a declared purpose while
  retaining residual risk and decision ownership.
  \item libkungfu and \texttt{.kungfu} preserve admitted work facts, Episodes,
  roots, exports, and recovery evidence; applications still own domain facts.
  \item the KFD Agent Hub profile carries bounded responsibility objects across
  independently owned products, with receiver-owned admission.
\end{enumerate}

The layers remain separable authorities. Buildchain does not invent product
facts or make the trust decision. KFD does not become a central Hub, identity
provider, database, or transport. Kungfu's JSON surfaces are edge projections,
not a second authoritative data plane.

\subsection{Conservative Context Projection}

A new Agent does not need every token from every prior session. It needs a
bounded projection that can be traced back to admitted Facts, causal Episodes,
declared perspective, continuing direction, and current authority. A useful
projection may summarize or omit material, but it must declare that loss and
must not upgrade an unknown, conflict, or withheld field into a verified fact.

The full Project Cut remains the round-trip authority. A model-specific context
pack is a replaceable view. If the view cannot preserve a load-bearing
distinction, the system must expose the loss or refuse the projection rather
than silently flattening it.

\subsection{Session and Agent Replacement}

The architecture treats sessions, models, and Agent processes as replaceable.
The work should survive:

\begin{itemize}
  \item context-window exhaustion or deliberate context reset;
  \item a new model or provider taking over the same bounded Assignment;
  \item process crash and recovery from the journal and content roots;
  \item movement between local and remote execution environments;
  \item human review between producing and continuing Agents; and
  \item exchange between independently owned Hubs that make their own
  admission decisions.
\end{itemize}

The successor does not trust the predecessor because both are called Agents.
It verifies the cut, evidence, authority, and receipt under its local policy.

\subsection{Failure Must Stay Visible}

Continuity is invalid if the next session starts from a missing Episode, stale
Atlas, mismatched receipt, incomplete parent acceptance, changed source after a
Claim, widened Warrant, conflicting successor, or unverifiable root. Kungfu
preserves such conditions as typed failure, conflict, unavailability, or
intentional withholding. Last-write-wins and confident prose are not recovery
strategies.
