\section{KFD and Independent Agent Hubs}

KFD---Kung Fu Decisions---is an open engineering standard for a small, testable
foundation for reliable action and continuity under uncertainty. It is a
canonical public decision registry, not a Kungfu product API, a central service,
a universal workflow language, or a belief test. Products, organizations,
humans, Agents, and other bounded systems can adopt exact decisions within a
declared scope and publish their own mappings, evidence, qualification, and
residual risk.\cite{kungfuKfd}

\subsection{The Foundation}

KFD begins with three commitments:

\begin{center}
\begin{tabular}{ll}
\toprule
KFD-1 & Facts must not drift. \\
KFD-2 & Trust must start from facts. \\
KFD-3 & Cooperation must start from trusted value. \\
\bottomrule
\end{tabular}
\end{center}

The later decisions make the foundation operational. Views remain bound to
declared perspectives. Primitive discovery separates genesis from
qualification. Real-world action keeps state, occurrence, and action
coordinates distinct. Numbered drafts then allocate emerging responsibility
for Atlas, Pursuit, Warrant, Decision and Admission, software work, and Project
settlement.

As of the alpha coordinate cited by this paper, the registry state is:

\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.13\textwidth}>{\raggedright\arraybackslash}p{0.15\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Decision & Status & Responsibility \\
\midrule
\texttt{KFD-1} & active & Non-drifting facts and verifiable coordinates. \\
\texttt{KFD-2} & active & Fact-bound trust, assessment, and residual risk. \\
\texttt{KFD-3} & active & Cooperation through visible value, constraints,
choices, and records. \\
\texttt{KFD-4} & active & Views bound to declared perspectives and loss. \\
\texttt{KFD-5} & active & Primitive genesis separated from qualification. \\
\texttt{KFD-6} & draft & Autonomous discovery grounded in causal
experience. \\
\texttt{KFD-7} & active & Fact--Episode separation and action responsibility
geometry. \\
\texttt{KFD-8} & draft & Atlas responsibility for admitted perspective. \\
\texttt{KFD-9} & draft & Pursuit responsibility for continuing direction. \\
\texttt{KFD-10} & draft & Explicit, bounded, revocable Warrant authority. \\
\texttt{KFD-11} & draft & Claim, Assessment, Decision, and Admission
separation. \\
\texttt{KFD-12} & draft & Initiative and Assignment separation in software
work. \\
\texttt{KFD-13} & draft & Project settlement that binds authorities without
absorbing them. \\
\bottomrule
\end{tabularx}
\normalsize

Active decisions are normative within their declared adoption scope. A numbered
draft has an allocated identity but an open activation gate. A pre-number KFD
Candidate remains non-normative lineage. Product evidence for Project Cut does
not silently activate KFD-13.

\subsection{The Hub Boundary}

An Agent Hub is a participant-owned control plane for execution, identity,
policy, accounts, models, user experience, admission, and customer
relationships. It may be a local process, device service, vendor cloud,
organizational system, or federation member. KFD standardizes only the
responsibility exchange between Hubs.

No KFD deployment requires one global identity provider, Hub registry,
database, transport, clock, or KFD cloud. One Hub may use \texttt{libkungfu};
another may implement the semantics independently. Each keeps its internal
workflow and local verdict authority.

\subsection{The Agent Hub Alpha Profile}

KFD publishes a transport-neutral Agent Hub alpha Profile. A Profile coordinate
binds its identifier, version, manifest digest, and repository commit. Peers
negotiate an exact capability intersection, then exchange rooted responsibility
proposals, candidate Fact admissions, supersession, completion Assessments, or
Warrant revocations. The same semantics can travel through a local call, IPC,
file, HTTP, gRPC, message bus, or offline bundle.\cite{kungfuAgentHub}

Every receiver retains the right and responsibility to verify authority,
disclosure, evidence, conflict, and policy before writing its verdict. Retries
are content-stable, conflicts stay visible, partial knowledge is typed, and
unknown required semantics fail closed.

The Profile is alpha and is not itself a numbered KFD. It is not stable
certification, proof of a conforming implementation, evidence of external vendor
adoption, or proof of plural-Hub interoperability. Its purpose is to make the
boundary implementable and falsifiable while independent builders gain real
integration evidence.
