\section{Current State, Adoption, and Roadmap}

This paper is an alpha positioning and architecture document. It recommends
immediate implementation work while keeping capability claims below the public
evidence ceiling.

\subsection{What Exists Today}

As of 21 July 2026, the public surfaces support the following statements:

\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.19\textwidth}>{\raggedright\arraybackslash}p{0.38\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Surface & Supported statement & Open boundary \\
\midrule
Project Cut & Protocol, settlement implementation, retained first-party Cuts,
and a qualified three-actor continuation case exist. & The complete ordinary
user product loop and v4 release qualification remain open. \\
\texttt{libkungfu} & Open source runtime code, exact-source quickstarts,
runtime Facts, Episodes, verification, recovery, and product-layer contracts
exist. & Builders should use source-pinned proofs of concept and cite exact
package and platform facts; broad production readiness is not claimed. \\
KFD & Package \texttt{1.0.0-alpha.40} publishes active KFD-1, 2, 3, 4, 5, and
7 plus numbered draft KFD-6 and KFD-8 through KFD-13. & Pre-stable meanings,
draft activation, adopter scope, and residual risk remain explicit. \\
Agent Hub Profile & Transport-neutral \texttt{0.1.0-alpha.1} schemas,
manifest, state model, and implementer guidance exist. & No stable
certification, external vendor adoption, or plural-Hub production proof. \\
Runtime Profile & A rooted 100-vector alpha suite, including 35 Core and 65
Experimental vectors, and two reference adapters make the contract executable.
& Passing is non-qualifying and binds only the exact adapter, suite, platform,
transcript, and report. \\
Buildchain & Artifact, package, source, publication, and release evidence is
used across the public Kungfu system. & Release evidence is not project
Admission, runtime authority, or proof of product meaning. \\
\bottomrule
\end{tabularx}
\normalsize

The fixed public dogfood snapshot at
\texttt{2026-07-21T04:45:00Z} records 2,740 merged public pull requests across
10 repositories in the preceding 30-day window and 148 retained public Project
Cuts with 148 valid receipts at the Kungfu source commit recorded in the
snapshot. These are
work and evidence counts, not feature counts, Agent identity counts, external
adoption, or proof that every review was an approval.\cite{kungfuDogfood}

\subsection{The Builder Path: Inspect, Embed, Prove, Connect}

\begin{enumerate}
  \item \textbf{Inspect.} Read the exact source-linked quickstart, KFD decision
  coordinates, Agent Hub Profile manifest, runtime facts, and known limits.
  Choose the smallest host-language path and define what data remains outside
  the adapter.
  \item \textbf{Embed.} Link \texttt{libkungfu}, initialize an isolated local
  runtime only through explicit product action, and project a narrow set of
  lifecycle events. Deliver Project Cut inspect, verify, settle, recover, and
  resume behavior inside the vendor's existing UX.
  \item \textbf{Prove.} Exercise clean initialization, deterministic roots,
  crash recovery, stale and conflicting candidates, revoked or widened
  Warrants, independent Claim assessment, and fresh-Agent continuation. Bind
  every public claim to exact source, suite, platform, evidence, and residual
  risk.
  \item \textbf{Connect.} Implement the participant-owned Hub adapter,
  negotiate an exact mutually supported Profile, exchange only the required
  responsibility evidence, and keep admission and verdict writing local.
\end{enumerate}

This is not a wait-for-stability sequence. Inspect, Embed, and the first Prove
loop should begin now against pinned alpha coordinates. Hub architecture and
policy work should proceed in parallel. Cross-Hub production claims should wait
for the exact interoperability evidence they require.

\subsection{Roadmap and Gates}

The near-term product gate is a low-friction time-to-first-cut experience and a
complete cut-to-cut continuation across a fresh Agent context. The runtime gate
is deterministic, recoverable behavior across supported host layers without
hidden authority in a projection. The Hub gate is receiver-owned admission,
capability negotiation, disclosure control, conflict preservation, and portable
exit across at least two independently owned implementations.

Public package installation, stable compatibility, platform coverage, and any
future certification program require their own release and governance evidence.
A future Kungfu Cloud may implement the same KFD boundary, but it is not a
prerequisite for adopting KFD or \texttt{libkungfu}, and this paper does not
announce such a product.

\subsection{Risks and Non-Claims}

The primary risks are premature certainty and collapsed boundaries:

\begin{itemize}
  \item treating a Project Cut as a replacement for Git, Atlas, Episode,
  policy, or decision authority;
  \item marketing runtime embedding as automatic KFD certification;
  \item rebuilding the runtime inside every Hub and creating incompatible local
  fact semantics;
  \item turning KFD into a central registry, cloud dependency, or mandatory
  universal ontology;
  \item exporting prompts, secrets, or private Episode bodies when rooted
  disclosure would suffice; and
  \item presenting first-party dogfood, reference adapters, or alpha suites as
  external adoption, endorsement, broad production readiness, or a
  multi-platform guarantee.
\end{itemize}

The safe alpha posture is ambitious in implementation and conservative in
claims: integrate now, publish exact evidence, expose failure, and let stable
promises follow independent qualification rather than precede it.
