\section{Conclusion}

The market is moving from Agents that answer inside a chat to Agents that carry
responsibility across real work. The decisive product question is no longer
only how intelligent one session can be. It is whether the work remains
verifiable, recoverable, and continuable after that session disappears.

Kungfu's answer begins with the user: the first object is a Project Cut, not a
transcript. The Cut states what the project formally became, what occurrence
and decision evidence supports it, which uncertainty remains, and where bounded
work may continue. A fresh Agent can verify that boundary instead of inheriting
an unverifiable story.

The answer continues with builders: embed \texttt{libkungfu} rather than
rebuilding the runtime. Keep the Hub, product experience, models, identity,
policy, cloud, admission, and customer relationship. Build the KFD boundary in
parallel so evidence and responsibility can move between independently owned
systems without creating one central authority.

The answer remains open: KFD is independently implementable, receiver verdicts
remain local, Buildchain owns release evidence rather than runtime truth, and
Project Cut binds authorities without absorbing them. The architecture is
designed for plural products, models, contexts, transports, and organizations.

The immediate alpha action is therefore clear:

\calloutbox{Start now}{Inspect the exact sources. Embed the runtime. Prove one
complete Project Cut continuation. Build the Hub boundary. Connect only through
evidence that both sides can verify.}

Give your Agent verified context. Keep the work when the chat ends.

If the product succeeds, Kungfu is not merely another Agent tool. Its public
KFD, Buildchain, trust, runtime, and Hub boundaries become an open Agent Supply
Chain that other products can evaluate and implement without yielding their
product authority. The current proof is intentionally narrower than that
future ecosystem; keeping the distinction visible is part of the trust model.
