\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\definecolor{KFBlack}{HTML}{111827}
\definecolor{KFSlate}{HTML}{374151}
\definecolor{KFGreen}{HTML}{0F766E}
\definecolor{KFLight}{HTML}{F3F7F6}
\definecolor{KFLighter}{HTML}{FAFBFB}
\definecolor{KFLine}{HTML}{D8E5E1}

\titleformat{\section}{\Large\bfseries\color{KFBlack}}{\thesection}{0.75em}{}
\titleformat{\subsection}{\large\bfseries\color{KFSlate}}{\thesubsection}{0.75em}{}
\setlist[itemize]{leftmargin=1.4em,itemsep=0.25em,topsep=0.35em}
\setlist[enumerate]{leftmargin=1.6em,itemsep=0.25em,topsep=0.35em}
\pagestyle{fancy}
\fancyhf{}
\lhead{\small Kungfu White Paper}
\rhead{\small The Session Is Not the Work}
\cfoot{\small\thepage}
\renewcommand{\headrulewidth}{0.3pt}

\newcommand{\calloutbox}[2]{%
  \begin{center}
  \fcolorbox{KFLine}{KFLight}{%
    \begin{minipage}{0.92\linewidth}
    \textbf{\color{KFGreen}#1}\par\vspace{0.35em}
    #2
    \end{minipage}
  }
  \end{center}
}

\newcommand{\signalrow}[2]{%
  \textbf{#1} & #2 \\
}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=black,
  pdftitle={Kungfu: The Session Is Not the Work},
  pdfauthor={Keren Dong; Kungfu Origin Technology Limited},
  pdfsubject={Verified continuity for agent work that outlives the chat}
}

\title{Kungfu: The Session Is Not the Work}
\author{Keren Dong\\Kungfu Origin Technology Limited\\\href{mailto:keren.dong@kungfu.link}{keren.dong@kungfu.link}}
\date{Alpha White Paper: July 2026}

\begin{document}

\begin{titlepage}
\thispagestyle{empty}
\raggedright
{\small\color{KFGreen}\textbf{KUNGFU WHITE PAPER | JULY 2026}}\par
\vspace{2.5cm}
{\Huge\bfseries\color{KFBlack} Kungfu: The Session Is Not the Work\par}
\vspace{0.8cm}
{\Large\color{KFSlate} Verified continuity for agent work that outlives the chat.\par}
\vspace{0.55cm}
{\normalsize\color{KFSlate} Project Cuts, \texttt{libkungfu}, and KFD: a local runtime and open responsibility protocol for long-running agent work.\par}
\vspace{1.2cm}
\calloutbox{User promise}{Give your agent verified context. Keep the work when the chat ends.}
\calloutbox{The move for Agent builders}{Embed \texttt{libkungfu} now. Deliver Project Cut continuity. Build your KFD-compatible Hub in parallel.}
\vspace{0.8cm}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.28\textwidth}>{\raggedright\arraybackslash}X}
\toprule
\signalrow{First user object}{A Project Cut: the verified point from which a project can continue.}
\signalrow{Reference runtime}{\texttt{libkungfu}: embeddable Facts, Episodes, verification, recovery, and Project Cut support.}
\signalrow{Open standard}{KFD: portable responsibility and evidence semantics across independently owned systems.}
\signalrow{Product boundary}{Each vendor keeps its interface, models, accounts, policy, cloud, and customer relationship.}
\signalrow{Current status}{Alpha interfaces and first-party evidence; source-pinned integration is encouraged, certification is not claimed.}
\bottomrule
\end{tabularx}
\vfill
{\large Keren Dong\par}
{\small Kungfu Origin Technology Limited \quad \href{mailto:keren.dong@kungfu.link}{keren.dong@kungfu.link}\par}
\end{titlepage}

\input{sections/00-executive-summary}

\input{sections/01-problem}
\input{sections/02-thesis}
\input{sections/03-principles}
\input{sections/04-architecture}
\input{sections/05-roadmap}
\input{sections/06-validation}
\input{sections/07-ecosystem}
\input{sections/08-risks}
\input{sections/09-conclusion}

\nocite{kungfuKfd,kungfuProjectCut,kungfuRuntime,kungfuAgentHub,kungfuBuilders,kungfuDogfood,kungfuBuildchain}
\bibliographystyle{plain}
\bibliography{references}

\end{document}
